---
title: "googleVis"
author: "Daniel Bies & Gonzalo Del Carpio"
date: "October 23, 2017"
output:
  html_document:
    self_contained: no
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(googleVis))
bcities=gudatavizfa17::bcities
```

#Introduction
## We were provided with data from Bloomberg's ranking of the top cities in the country. We analyzed this data and presented it below.

```{r}
facetchart=gather(bcities, "Variable", "Values", 1,3:13)
facetchart=facetchart[facetchart$Variable!="City",]
facetchart$Values=as.numeric(facetchart$Values)
```

```{r}
ggplot(facetchart,aes(x=Rank, y=Values)) + geom_point(size=.5)+facet_wrap(~Variable, scales = "free") + geom_smooth(method="lm") + labs(list(title= "Variable Correlation with City Rank", x="Rank", y="Variable"))
```



####After looking at the data, it was clear that the variable with the highest correlation to rank was graduate degree percentage. It seems that the makers of this ranking valued intelligence highly in cities, as there is a clear increase in percentage as the ranks get better. There was also a minor correlation with sports teams and having a higher ranking. 


###To make the latitude and longitude compatible for plotting the cities, a separating function was used.

```{r}
bcities$latlong=paste(bcities$lat,bcities$lon,sep=":")
```


###The plot below shows the cities from the dataset, plotted over a map of the US. 

```{r results= "asis"}
Geo=gvisGeoChart(bcities, "latlong", "Rank", options = list(region="US", dataMode= "markers",resolution= "provinces", width= 800, height=800, sizeAxis = '{minValue: 1,  maxSize: 3}'))
Geo
```



```{r}
bcities$Statecity= c("California", "Alaska", "Nebraska", "Missouri", "Ohio", "Virginia","Arizona", "Arizona", "Nevada", "Texas", "Virginia", "North Carolina", "Oklahoma", "Indiana", "Colorado", "Florida", "Nebraska", "California", "New York", "California", "Texas", "Maryland", "Illinois", "Washington", "Wisconsin", "Kentucky", "Pennsylvania", "Oklahoma", "Texas", "Ohio", "Ohio", "Hawaii", "North Carolina", "Wisconsin", "Georgia", "Kansas", "Lousiana", "Tennessee", "Minnesota", "Pennsylvania", "Minnesota", "California", "Texas", "New York", "Colorado", "Oregon", "Massachusetts", "District of Columbia", "Washington", "California")
```

###Dataset to count how many number of cities corresponds in each state.

```{r}
Countstate = bcities %>% group_by(Statecity) %>% summarise(Count = n())
Countstate$Count <- as.numeric(Countstate$Count)
Countstate$Statecity <- as.factor(Countstate$Statecity)
str(Countstate)
```

###Graphing an interactive map of the US by the top cities within each state we are able to tell that California leads all the other states in the amount of cities from the list.

```{r results='asis'}
States <- gvisGeoChart(Countstate,"Statecity", "Count", options=list(region="US", displayMode="regions", resolution="provinces",
width=800, height=800))
States
```